Predicting Infection Outbreak Dynamics in Toronto Healthcare Institutions: A Bayesian Approach

### 2024-12-15 paper/paper.qmd
Update paper.qmd

```{r}
cleaned_data |> 
  ggplot(aes(x = `Outbreak Setting`, fill = `Type of Outbreak`)) +
  geom_bar(position = "fill") +
  coord_flip() +
  labs(
    title = "Proportion of Outbreak Types by Setting",
    x = "Healthcare Setting",
    y = "Proportion"
  ) +
  theme_minimal()
```{r}

@@

```{r}
cleaned_data |> 
  ggplot(aes(x = Duration, fill = `Causative Agent-1`, color = `Causative Agent-1`)) +
  geom_density(alpha = 0.3) +
  facet_wrap(~ `Outbreak Setting`, scales = "free_y") +
  labs(
    title = "Outbreak Duration by Causative Agent and Setting",
    x = "Outbreak Duration (days)",
    y = "Density",
    fill = "Causative Agent",
    color = "Causative Agent"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    legend.text = element_text(size = 8),
    legend.title = element_text(size = 10)
  )
```{r}

>>>>

```{r}
cleaned_data |> 
  ggplot(aes(x = `Outbreak Setting`, fill = `Type of Outbreak`)) +
  geom_bar(position = "fill") +
  coord_flip() +
  labs(
    title = "Proportion of Outbreak Types by Setting",
    x = "Healthcare Setting",
    y = "Proportion"
  ) +
  theme_minimal()
```

@@

```{r}
cleaned_data |> 
  ggplot(aes(x = Duration, fill = `Causative Agent-1`, color = `Causative Agent-1`)) +
  geom_density(alpha = 0.3) +
  facet_wrap(~ `Outbreak Setting`, scales = "free_y") +
  labs(
    title = "Outbreak Duration by Causative Agent and Setting",
    x = "Outbreak Duration (days)",
    y = "Density",
    fill = "Causative Agent",
    color = "Causative Agent"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    legend.text = element_text(size = 8),
    legend.title = element_text(size = 10)
  )
```
